---
title: 'Trade Policy Test Bank'
author: 'Mauricio "Pacha" Vargas Sepúlveda'
date: 'Last update: `r Sys.time()`'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
library(tradepolicy)
```

# Partial equilibrium

## Elasticity

### Question 1

Use the next code to create the dataset `elasticity_data`:

```{r q1}
elasticity_data <- agtpa_applications %>% 
  filter(
    year == 2006,
    trade > 0,
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  group_by(exporter, year) %>% 
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>% 
  group_by(importer, year) %>% 
  mutate(
    e = sum(trade),
    log_e = log(e)
  ) %>% 
  mutate(log_trade = log(trade), log_dist = log(dist))
```

Then fit the model `log_trade ~ log_dist + cntg + lang + clny + log_y + log_e`. 

What can you say about `log_dist` in terms of elasticities?

a) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the estimated coefficient is less than one.
b) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the absolute value of the estimated coefficient is less than one.
c) We need more information.
d) None of the above.

### Question 2

Use the next code to create the dataset `elasticity_data`:

```{r q2}
elasticity_data <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2), 
    trade > 0,
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  group_by(exporter, year) %>% 
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>% 
  group_by(importer, year) %>% 
  mutate(
    e = sum(trade),
    log_e = log(e)
  ) %>% 
  mutate(log_trade = log(trade), log_dist = log(dist))
```

Then fit the model `log_trade ~ log_dist + cntg + lang + clny + log_y + log_e`. 

What can you say about `log_dist` in terms of elasticities?

a) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the estimated coefficient is less than one.
b) The value $\beta_{\text{log dist}}$ tells us that `trade` is elastic to `distance`, as the absolute value of the estimated coefficient is more than one.
c) We need more information.
d) None of the above.

### Question 3

Use the next code to create the dataset `elasticity_data`:

```{r q3}
elasticity_data <- agtpa_applications %>% 
  filter(
    year == 2002,
    trade > 0,
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  group_by(exporter, year) %>% 
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>% 
  group_by(importer, year) %>% 
  mutate(
    e = sum(trade),
    log_e = log(e)
  ) %>% 
  mutate(log_trade = log(trade), log_dist = log(dist))
```

Then fit the model `log_trade ~ log_dist + cntg + lang + clny + log_y + log_e`. 

What can you say about `log_dist` in terms of elasticities?

a) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the estimated coefficient is less than one.
b) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the absolute value of the estimated coefficient is less than one.
c) We need more information.
d) None of the above.

### Question 4

Use the next code to create the dataset `elasticity_data`:

```{r q4}
elasticity_data <- agtpa_applications %>% 
  filter(
    year == 2002,
    trade > 0,
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  group_by(exporter, year) %>% 
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>% 
  group_by(importer, year) %>% 
  mutate(
    e = sum(trade),
    log_e = log(e)
  ) %>% 
  mutate(log_trade = log(trade), log_dist = log(dist))
```

Then fit the model `log_trade ~ log_dist + cntg + lang + clny + log_y + log_e`. 

What can you say about `log_dist` in terms of elasticities?

a) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the estimated coefficient is less than one.
b) The value $\beta_{\text{log dist}}$ tells us that `trade` is inelastic to `distance`, as the absolute value of the estimated coefficient is less than one.
c) We need more information.
d) None of the above.

## RESET test

### Question 5

Run the next code to obtain a regression summary:

```{r q5}
ch1_application1_2 <- agtpa_applications %>%
  filter(year %in% seq(1986, 2006, 4))

ch1_application1_2 <- ch1_application1_2 %>%
  mutate(
    log_trade = log(trade),
    log_dist = log(dist)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Create Yit
  group_by(exporter, year) %>%
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>%

  # Create Eit
  group_by(importer, year) %>%
  mutate(
    e = sum(trade),
    log_e = log(e)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Replicate total_e
  group_by(exporter, year) %>%
  mutate(total_e = sum(e)) %>%
  group_by(year) %>%
  mutate(total_e = max(total_e)) %>%

  # Replicate rem_exp
  group_by(exporter, year) %>%
  mutate(
    remoteness_exp = sum(dist *  total_e / e),
    log_remoteness_exp = log(remoteness_exp)
  ) %>%

  # Replicate total_y
  group_by(importer, year) %>%
  mutate(total_y = sum(y)) %>%
  group_by(year) %>%
  mutate(total_y = max(total_y)) %>%

  # Replicate rem_imp
  group_by(importer, year) %>%
  mutate(
    remoteness_imp = sum(dist / (y / total_y)),
    log_remoteness_imp = log(remoteness_imp)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # This merges the columns exporter/importer with year
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  filter(exporter != importer)

my_summary <- tp_summary_app_1(
  formula = "log_trade ~ log_dist + cntg + lang + clny + log_y + log_e",
  data = filter(ch1_application1_2, trade > 0),
  method = "ols"
)

my_summary
```

What can you say about the RESET test p-value?

a) The model doesn't pass the misspecification test because the obtained p-value is below the critical p-value 0.05 (or any other common value).
b) The model passes the misspecification test because the obtained p-value is below the critical p-value 0.05 (or any other common value).
c) We need more information
d) None of the above

### Question 6

We are given the next regression summary:

```{r q6, echo=FALSE}
ch1_application1_2 <- agtpa_applications %>%
  filter(year %in% seq(1986, 2006, 4))

ch1_application1_2 <- ch1_application1_2 %>%
  mutate(
    log_trade = log(trade),
    log_dist = log(dist)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Create Yit
  group_by(exporter, year) %>%
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>%

  # Create Eit
  group_by(importer, year) %>%
  mutate(
    e = sum(trade),
    log_e = log(e)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Replicate total_e
  group_by(exporter, year) %>%
  mutate(total_e = sum(e)) %>%
  group_by(year) %>%
  mutate(total_e = max(total_e)) %>%

  # Replicate rem_exp
  group_by(exporter, year) %>%
  mutate(
    remoteness_exp = sum(dist *  total_e / e),
    log_remoteness_exp = log(remoteness_exp)
  ) %>%

  # Replicate total_y
  group_by(importer, year) %>%
  mutate(total_y = sum(y)) %>%
  group_by(year) %>%
  mutate(total_y = max(total_y)) %>%

  # Replicate rem_imp
  group_by(importer, year) %>%
  mutate(
    remoteness_imp = sum(dist / (y / total_y)),
    log_remoteness_imp = log(remoteness_imp)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # This merges the columns exporter/importer with year
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  filter(exporter != importer)

my_summary <- tp_summary_app_1(
  formula = "log_trade ~ log_dist + cntg + lang + clny + log_y + log_e +
    log_remoteness_exp + log_remoteness_imp",
  data = filter(ch1_application1_2, trade > 0),
  method = "ols"
)

my_summary
```

What can you say about the RESET test p-value?

a) The model doesn't pass the misspecification test because the obtained p-value is below the critical p-value 0.05 (or any other common value).
b) The model passes the misspecification test because the obtained p-value is below the critical p-value 0.05 (or any other common value).
c) We need more information
d) None of the above

### Question 7

We are given the next regression summary:

```{r q7, echo=FALSE}
ch1_application1_2 <- agtpa_applications %>%
  filter(year %in% seq(1986, 2006, 4))

ch1_application1_2 <- ch1_application1_2 %>%
  mutate(
    log_trade = log(trade),
    log_dist = log(dist)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Create Yit
  group_by(exporter, year) %>%
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>%

  # Create Eit
  group_by(importer, year) %>%
  mutate(
    e = sum(trade),
    log_e = log(e)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Replicate total_e
  group_by(exporter, year) %>%
  mutate(total_e = sum(e)) %>%
  group_by(year) %>%
  mutate(total_e = max(total_e)) %>%

  # Replicate rem_exp
  group_by(exporter, year) %>%
  mutate(
    remoteness_exp = sum(dist *  total_e / e),
    log_remoteness_exp = log(remoteness_exp)
  ) %>%

  # Replicate total_y
  group_by(importer, year) %>%
  mutate(total_y = sum(y)) %>%
  group_by(year) %>%
  mutate(total_y = max(total_y)) %>%

  # Replicate rem_imp
  group_by(importer, year) %>%
  mutate(
    remoteness_imp = sum(dist / (y / total_y)),
    log_remoteness_imp = log(remoteness_imp)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # This merges the columns exporter/importer with year
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  filter(exporter != importer)

my_summary <- tp_summary_app_1(
  formula = "log_trade ~ log_dist + cntg + lang + clny | exp_year + imp_year",
  data = filter(ch1_application1_2, trade > 0),
  method = "ols"
)

my_summary
```

What can you say about the RESET test p-value?

a) The model doesn't pass the misspecification test because the obtained p-value is below the critical p-value 0.05 (or any other common value).
b) The model passes the misspecification test because the obtained p-value is below the critical p-value 0.05 (or any other common value).
c) We need more information
d) None of the above

### Question 8

We are given the next regression summary:

```{r q8, echo=FALSE}
ch1_application1_2 <- agtpa_applications %>%
  filter(year %in% seq(1986, 2006, 4))

ch1_application1_2 <- ch1_application1_2 %>%
  mutate(
    log_trade = log(trade),
    log_dist = log(dist)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Create Yit
  group_by(exporter, year) %>%
  mutate(
    y = sum(trade),
    log_y = log(y)
  ) %>%

  # Create Eit
  group_by(importer, year) %>%
  mutate(
    e = sum(trade),
    log_e = log(e)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # Replicate total_e
  group_by(exporter, year) %>%
  mutate(total_e = sum(e)) %>%
  group_by(year) %>%
  mutate(total_e = max(total_e)) %>%

  # Replicate rem_exp
  group_by(exporter, year) %>%
  mutate(
    remoteness_exp = sum(dist *  total_e / e),
    log_remoteness_exp = log(remoteness_exp)
  ) %>%

  # Replicate total_y
  group_by(importer, year) %>%
  mutate(total_y = sum(y)) %>%
  group_by(year) %>%
  mutate(total_y = max(total_y)) %>%

  # Replicate rem_imp
  group_by(importer, year) %>%
  mutate(
    remoteness_imp = sum(dist / (y / total_y)),
    log_remoteness_imp = log(remoteness_imp)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  # This merges the columns exporter/importer with year
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year)
  )

ch1_application1_2 <- ch1_application1_2 %>%
  filter(exporter != importer)

my_summary <- tp_summary_app_1(
  formula = "trade ~ log_dist + cntg + lang + clny | exp_year + imp_year",
  data = ch1_application1_2,
  method = "ppml"
)

my_summary
```

What can you say about the RESET test p-value?

a) The model doesn't pass the misspecification test because the obtained p-value is above the critical p-value 0.05 (or any other common value).
b) The model passes the misspecification test because the obtained p-value is above the critical p-value 0.05 (or any other common value).
c) We need more information
d) None of the above

## Distance puzzle

### Question 9

Suppose that now we are interested in the OLS version of the distance puzzle. Complete the next code to fit the model:

```{r q9, eval = FALSE}
ols_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1)
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "log_trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 + cntg +
    lang + clny | exp_year + imp_year",
  data = filter(ols_puzzle, importer != exporter, trade > 0),
  method = "ols"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) show a significant decrease on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 10

Suppose that now we are interested in the OLS version of the distance puzzle. Complete the next code to fit the model:

```{r q10, eval = FALSE}
ols_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1)
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "log_trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 + cntg +
    lang + clny | exp_year + imp_year",
  data = filter(ols_puzzle, importer != exporter, trade > 0),
  method = "ols"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) show a significant decrease on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 11

Suppose that now we are interested in the OLS version of the distance puzzle. Complete the next code to fit the model:

```{r q11, eval = FALSE}
ols_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1)
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "log_trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 + cntg +
    lang + clny | exp_year + imp_year",
  data = filter(ols_puzzle, importer != exporter, trade > 0),
  method = "ols"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) show a significant decrease on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 12

Suppose that now we are interested in the OLS version of the distance puzzle. Complete the next code to fit the model:

```{r q12, eval = FALSE}
ols_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1)
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "log_trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 + cntg +
    lang + clny | exp_year + imp_year",
  data = filter(ols_puzzle, importer != exporter, trade > 0),
  method = "ols"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) show a significant decrease on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 13

Suppose that now we are interested in the PPML version of the distance puzzle. Complete the next code to fit the model:

```{r q13, eval = FALSE}
ppml_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny | exp_year + imp_year",
  data = filter(ppml_puzzle, importer != exporter),
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 14

Suppose that now we are interested in the PPML version of the distance puzzle. Complete the next code to fit the model:

```{r q14, eval = FALSE}
ppml_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny | exp_year + imp_year",
  data = filter(ppml_puzzle, importer != exporter),
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 15

Suppose that now we are interested in the PPML version of the distance puzzle. Complete the next code to fit the model:

```{r q15, eval = FALSE}
ppml_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny | exp_year + imp_year",
  data = filter(ppml_puzzle, importer != exporter),
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 16

Suppose that now we are interested in the PPML version of the distance puzzle. Complete the next code to fit the model:

```{r q16, eval = FALSE}
ppml_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny | exp_year + imp_year",
  data = filter(ppml_puzzle, importer != exporter),
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 17

Suppose that now we are interested in the Internal Distance version of the distance puzzle. Complete the next code to fit the model:

```{r q17, eval = FALSE}
intra_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra | exp_year + imp_year",
  data = intra_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 18

Suppose that now we are interested in the Internal Distance version of the distance puzzle. Complete the next code to fit the model:

```{r q18, eval = FALSE}
intra_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra | exp_year + imp_year",
  data = intra_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 19

Suppose that now we are interested in the Internal Distance version of the distance puzzle. Complete the next code to fit the model:

```{r q19, eval = FALSE}
intra_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra | exp_year + imp_year",
  data = intra_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 20

Suppose that now we are interested in the Internal Distance version of the distance puzzle. Complete the next code to fit the model:

```{r q20, eval = FALSE}
intra_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra | exp_year + imp_year",
  data = intra_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 21

Suppose that now we are interested in the Internal Distance and Home Bias version of the distance puzzle. Complete the next code to fit the model:

```{r q21, eval = FALSE}
brdr_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra + smctry | exp_year + imp_year",
  data = brdr_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 22

Suppose that now we are interested in the Internal Distance and Home Bias version of the distance puzzle. Complete the next code to fit the model:

```{r q22, eval = FALSE}
brdr_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra + smctry | exp_year + imp_year",
  data = brdr_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 23

Suppose that now we are interested in the Internal Distance and Home Bias version of the distance puzzle. Complete the next code to fit the model:

```{r q23, eval = FALSE}
brdr_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra + smctry | exp_year + imp_year",
  data = brdr_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 24

Suppose that now we are interested in the Internal Distance and Home Bias version of the distance puzzle. Complete the next code to fit the model:

```{r q24, eval = FALSE}
brdr_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + log_dist_intra + smctry | exp_year + imp_year",
  data = brdr_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 25

Suppose that now we are interested in the Fixed Effects version of the distance puzzle. Complete the next code to fit the model:

```{r q25, eval = FALSE}
fe_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + intra_pair | exp_year + imp_year",
  data = fe_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 26

Suppose that now we are interested in the Fixed Effects version of the distance puzzle. Complete the next code to fit the model:

```{r q26, eval = FALSE}
fe_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + intra_pair | exp_year + imp_year",
  data = fe_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 27

Suppose that now we are interested in the Fixed Effects version of the distance puzzle. Complete the next code to fit the model:

```{r q27, eval = FALSE}
fe_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + intra_pair | exp_year + imp_year",
  data = fe_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

### Question 28

Suppose that now we are interested in the Fixed Effects version of the distance puzzle. Complete the next code to fit the model:

```{r q28, eval = FALSE}
fe_puzzle <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    # variables for OLS
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("log_dist_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    smctry = ifelse(importer != exporter, 0, 1),
    
    # PPML specific variables
    log_dist_intra = log_dist * smctry,
    intra_pair = ifelse(exporter == importer, exporter, "inter")
  ) %>% 
  spread(year, log_dist, fill = 0) %>% 
  mutate(across(log_dist_2000:log_dist_2006, ~ .x * (1 - smctry)))

tp_summary_app_2(
  formula = "trade ~ ___ + log_dist_2000 + ___ + log_dist_2006 +   
    cntg + lang + clny + intra_pair | exp_year + imp_year",
  data = fe_puzzle,
  method = "ppml"
)
```

What can we say about this model?

a) The change of the effects of distance (and it's associated p-value) shows a significant decrease in the effects of distance on trade between 2000 and 2006.
b) The impact of internal distance on domestic sales is much smaller as compared to the distance effects on international trade.
c) A and B allows us to conclude that this model solves the "distance puzzle".
d) None of the above.

## Regional Trade Agreements

### Question 29

Suppose that now we are interested in the phasing-in effects of RTAs. Complete the next code to fit the corresponding model:

```{r q29, eval = FALSE}
phsng_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

phsng_rta <- phsng_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 |
    exp_year + imp_year + pair_id_2",
  data = filter(phsng_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is positive and not statistically significant.
b) show a significant decrease on trade.
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 30

Suppose that now we are interested in the phasing-in effects of RTAs. Complete the next code to fit the corresponding model:

```{r q30, eval = FALSE}
phsng_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

phsng_rta <- phsng_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 |
    exp_year + imp_year + pair_id_2",
  data = filter(phsng_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is positive and not statistically significant.
b) Shows an significant decrease on trade.
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 31

Suppose that now we are interested in the phasing-in effects of RTAs. Complete the next code to fit the corresponding model:

```{r q31, eval = FALSE}
phsng_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

phsng_rta <- phsng_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 |
    exp_year + imp_year + pair_id_2",
  data = filter(phsng_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is statistically zero.
b) The total effect of RTAs between 2000 and 2006 in trade is positive and statistically significant.
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 32

Suppose that now we are interested in the phasing-in effects of RTAs. Complete the next code to fit the corresponding model:

```{r q32, eval = FALSE}
phsng_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

phsng_rta <- phsng_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 |
    exp_year + imp_year + pair_id_2",
  data = filter(phsng_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is positive and not statistically significant.
b) show a significant decrease on trade
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 33

Suppose that now we are interested in globalization effects. Complete the next code to fit the corresponding model:

```{r q33, eval = FALSE}
gblzn_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("CHN","JPN","KOR")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

gblzn_rta <- gblzn_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 +
    intl_border_2000 + ___ + intl_border_2006 |
    exp_year + imp_year + pair_id_2",
  data = filter(gblzn_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is negative and not statistically significant.
b) Not all of the RTAs estimated coefficients are positive and significant, at least one is negative and/or not statistically significant.
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 34

Suppose that now we are interested in globalization effects. Complete the next code to fit the corresponding model:

```{r q34, eval = FALSE}
gblzn_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","FRA","USA")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

gblzn_rta <- gblzn_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 +
    intl_border_2000 + ___ + intl_border_2006 |
    exp_year + imp_year + pair_id_2",
  data = filter(gblzn_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is negative and not statistically significant.
b) Not all of the RTAs estimated coefficients are positive and significant, at least one is negative and/or not statistically significant.
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 35

Suppose that now we are interested in globalization effects. Complete the next code to fit the corresponding model:

```{r q35, eval = FALSE}
gblzn_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("AUS","IND","CHN")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

gblzn_rta <- gblzn_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 +
    intl_border_2000 + ___ + intl_border_2006 |
    exp_year + imp_year + pair_id_2",
  data = filter(gblzn_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is negative and not statistically significant.
b) Not all of the RTAs estimated coefficients are positive and significant, at least one is negative and/or not statistically significant.
c) A and B.
d) The model can't be estimated because of collinearity.

### Question 36

Suppose that now we are interested in globalization effects. Complete the next code to fit the corresponding model:

```{r q36, eval = FALSE}
gblzn_rta <- agtpa_applications %>% 
  filter(
    year %in% seq(2000, 2006, 2),
    exporter %in% c("THA","PHL","IDN")
  ) %>% 
  mutate(
    exp_year = paste0(exporter, year),
    imp_year = paste0(importer, year),
    year = paste0("intl_border_", year),
    log_trade = log(trade),
    log_dist = log(dist),
    intl_brdr = ifelse(exporter == importer, pair_id, "inter"),
    intl_brdr_2 = ifelse(exporter == importer, 0, 1),
    pair_id_2 = ifelse(exporter == importer, "0-intra", pair_id)
  ) %>% 
  spread(year, intl_brdr_2, fill = 0)

gblzn_rta <- gblzn_rta %>% 
  group_by(pair_id) %>% 
  mutate(sum_trade = sum(trade)) %>% 
  ungroup()

tp_summary_app_3(
  formula = "trade ~ ___ + rta + rta_lag4 + rta_lag8 + rta_lag12 +
    intl_border_2000 + ___ + intl_border_2006 |
    exp_year + imp_year + pair_id_2",
  data = filter(gblzn_rta, sum_trade > 0),
  method = "ppml"
)
```

What can we say about this model?

a) The total effect of RTAs between 2000 and 2006 in trade is negative and not statistically significant.
b) Not all of the RTAs estimated coefficients are positive and significant, at least one is negative and/or not statistically significant.
c) A and B.
d) The model can't be estimated because of collinearity.

# General equilibrium

## Baseline model

### Question 37

Suppose we are interested in solving the baseline model with *Australia* as the reference country. 

Complete the next code in order to be able to pick the right alternative:

```{r q37, eval = FALSE}
# Baseline dataset

baseline_data <- agtpa_applications %>% 
  filter(year == 2006) %>% 
  mutate(
    log_dist = log(dist),
    intl = ifelse(exporter != importer, 1, 0),
    exporter = ifelse(exporter == "AUS", ___, exporter),
    importer = ifelse(___)
  ) %>% 
  
  # Create Yit
  group_by(exporter, year) %>% 
  mutate(y = sum(trade)) %>% 
  
  # Create Eit
  group_by(___) %>% 
  mutate(e = sum(trade)) %>% 
  
  # Create Er
  ungroup() %>% 
  mutate(e_r = max(ifelse(importer == ___, e, NA), na.rm = T))

# Baseline model WITHOUT intercept

fepois(
  trade ~ ___ 0 + log_dist + cntg + intl | exporter + importer,
  data = ___
)
```

What can you say about the estimate and clustered standard error for the contiguity variable?

a) The estimate is 0.674 and the std. error is 0.045.
b) The estimate is 0.674 and the std. error is 0.140.
c) We need more information.
d) None of the above.

### Question 38

Suppose we are interested in solving the baseline model with *Australia* as the reference country. 

Complete the next code in order to be able to pick the right alternative:

```{r q38, eval = FALSE}
# Baseline dataset

baseline_data <- agtpa_applications %>% 
  filter(year == 2006) %>% 
  mutate(
    log_dist = log(dist),
    intl = ifelse(exporter != importer, 1, 0),
    exporter = ifelse(exporter == "AUS", ___, exporter),
    importer = ifelse(___)
  ) %>% 
  
  # Create Yit
  group_by(exporter, year) %>% 
  mutate(y = sum(trade)) %>% 
  
  # Create Eit
  group_by(___) %>% 
  mutate(e = sum(trade)) %>% 
  
  # Create Er
  ungroup() %>% 
  mutate(e_r = max(ifelse(importer == ___, e, NA), na.rm = T))

# Baseline model WITHOUT intercept

fit_baseline_data <- fepois(
  trade ~ log_dist + cntg + intl | exporter + importer,
  data = ___
  cluster = ___
)
```

Which of the next codes is correct to join both the original baseline dataset and the fixed effects?

a) `baseline_data %>% left_join(fixef(fit_baseline_data), "exporter")`.
b) `baseline_data %>% mutate(fe_importer_cfl = fixef(fit_counterfactual_app1)$importer[importer])`
c) `baseline_data %>% mutate(fe_exporter_cfl = fixef(fit_counterfactual_app1)$exporter[exporter])`.
d) B and C.

### Question 39

Suppose we are interested in solving the baseline model with *Australia* as the reference country. 

Complete the next code in order to be able to pick the right alternative:

```{r q39, eval = FALSE}
# Baseline dataset

baseline_data <- agtpa_applications %>% 
  filter(year == 2006) %>% 
  mutate(
    log_dist = log(dist),
    intl = ifelse(exporter != importer, 1, 0),
    exporter = ifelse(exporter == "AUS", ___, exporter),
    importer = ifelse(___)
  ) %>% 
  
  # Create Yit
  group_by(exporter, year) %>% 
  mutate(y = sum(trade)) %>% 
  
  # Create Eit
  group_by(___) %>% 
  mutate(e = sum(trade)) %>% 
  
  # Create Er
  ungroup() %>% 
  mutate(e_r = max(ifelse(importer == ___, e, NA), na.rm = T))

# Baseline model WITHOUT intercept

fit_baseline_data <- fepois(
  trade ~ log_dist + cntg + intl | exporter + importer,
  data = ___,
  cluster = ___
)

# Fixed effects data

baseline_data <- baseline_data %>%
  mutate(
    fe_exporter = fixef(___)$exporter[___],
    fe_importer = fixef(___)$importer[___]
  )

# Obtain bilateral trade costs and multilateral resistances

baseline_data <- baseline_data %>% 
  mutate(
    tij_bln = exp(___$___[___] * log_dist +
                  ___ * cntg +
                  ___ * intl),
  
    # outward multilateral resistance (omr)
    omr_bln = y * (e_r / exp(fe_exporter)),
    
    # inward multilateral resistance (imr)
    imr_bln = e / (exp(fe_importer) * e_r)
  )

# Obtain the estimated international trade for given output and expenditures

baseline_data <- baseline_data %>% 
  mutate(tradehat_bln = predict(___, ___)) %>% 
  group_by(___) %>% 
  mutate(xi_bln = sum(tradehat_bln * (exporter != importer))) %>% 
  ungroup()
```

What is the estimated international trade for *Australia*:

a) 77,417.
b) 34,708.
c) 109,914.
d) We need more information.

## Question 40

Observe the next plot that summarizes a full GEPPML model. This plot depicts the changes of real GDP associated with the removal of international borders and decomposes these changes into effects on the consumers (via the inward multilateral resistances) and on the producers (via the factory-gate prices) for a sample of countries.

```{r q40, echo=FALSE}
ge_twb <- readRDS("ge_twb.rds")

g <- ggplot(data = ge_twb) +
  geom_point(aes(x = log_y, y = change_imr_full, color = "1")) +
  geom_point(aes(x = log_y, y = change_price_full, color = "2")) +
  geom_point(aes(x = log_y, y = rgdp, color = "3")) +
  labs(
    x = "Log value of output",
    y = "Percent changes",
    title = "Effects of abolishing international borders on real GDP"
  ) +
  scale_color_manual(
    labels = c(
      "-(inward multilateral resistances)",
      "Factory-gate price",
      "Real GDP"
    ),
    values = c("red", "green", "blue")
  )

g
```

What can you conclude based on what you learned about gravity models in this course?

a) The *full endowment* general equilibrium effects on real GDP are large.
b) The real GDP effects vary significantly across the countries in the sample.
c) It is clear that for some countries there is a larger benefit from the removal of borders in terms of exports.
d) All of the above.
